idealista18: A data package with real estate information in three major Spanish markets from the Idealista database\tnoteref{tnote1}

### 2021-07-04 data-in-brief/dib-idealista18.tex
A first version of the abstract section Value of data section

%%Affiliations
\address[1]{Affiliation 1, Address, City and Postal Code, Country}
\address[2]{Affiliation 2, Address, City and Postal Code, Country}
\address[3]{School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada}

@@

\begin{abstract}
%%%%
Please Type your abstract here.

\noindent[The Abstract should describe the data collection process, the analysis
performed, the data, and their reuse potential. It should not provide
conclusions or interpretive insights. If your article is being
submitted via another Elsevier journal as a co-submission, please cite
this research article in the abstract.

\noindent\textbf{Tip:} do not use words such as
`study', `results', and `conclusions' because a data article should be
describing your data only.  Min 100 words - Max 500 words.]
%%%%
\end{abstract}

@@

[Provide 3-6 bullet points explaining why these data are of value to the scientific community.
Bullet points 1-3 must specifically answer the questions next to the bullet point,
but do not include the question itself in your answer. You may
provide up to three additional bullet points to outline the value of these data.
Please keep points brief, with ideally no more than 400 characters for each point.]

\begin{itemize}
\itemsep=0pt
\parsep=0pt
\item Your first bullet point must explain why these data are useful or important?
\item Your second bullet point must explain who can benefit from these data?
\item Your third point bullet must explain how these data might be used/reused for
further insights and/or development of experiments.
\item In the next three points you may like to explain how these data could
potentially make an impact on society and highlight any other additional value of these data.
\item ....
\end{itemize}

>>>>

%%Affiliations
\address[1]{idealista, Plaza de las Cortes 5, 28014 Madrid, Spain}
\address[2]{Facultad de CC de la Empresa, C/ Real, 3. 30201 Cartagena, Murcia (Spain)}
\address[3]{School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada}

@@

\begin{abstract}
%%%%
This dataset contains three items for each of the three major cities in Spain: Madrid, Barcelona and Valencia. First real estate listings published on idealista portal in 2018. All listings have been enriched with cadastral information (i.e. building year of construction, built quality materials grade) plus some geographical features such as
distance to relevant city areas and the coordinates themselves. To comply with european personal protection laws, we have processeed some sensible variables yet preserving their spatial properties. The second and third items are a list of points of interest and the administrative boundaries for each municipality.
This dataset is suitable to house market analysis, hedonic house price models and other spatial research related with real estate markets.

\textbf{<falta cita/referencia al artículo>}

%\noindent[The Abstract should describe the data collection process, the analysis
%performed, the data, and their reuse potential. It should not provide
%conclusions or interpretive insights. If your article is being
%submitted via another Elsevier journal as a co-submission, please cite
%this research article in the abstract.

%\noindent\textbf{Tip:} do not use words such as
%`study', `results', and `conclusions' because a data article should be
%describing your data only.  Min 100 words - Max 500 words.]

%%%%
\end{abstract}

@@

\begin{itemize}
\itemsep=0pt
\parsep=0pt
  \item A cleaned and enriched dataset consisting of real estate listings for three major cities in Spain, constructed to analyze the impacto of using machine learning models to identify spatial market segments to build house price hedonic models.
  \item The dataset can be used to extend the topic of market segments automatic or semi-automatic identification.
    \item Official boundaries combined with spatial patterns can be used to analyse the suitability of these boundaries for real estate value purposes.
  \item The dataset can be enlarged with complementary information to develop hedonic models.
  \item The data can be processed by quantitative analysis and statistical modeling to study the different factors that affect house prices in the three areas.
  \item Identification of spatial patterns in the real estate scope using the geo-referenced data points. For either value or urban patterns discovery.
\end{itemize}
